---
title: "Getting Started with sparkredshift"
author: "Daniel Emaasit"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE, eval = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Read data from Amazon Redshift into Spark DataFrames

## What is sparkredshift?

sparkredshipt is an extension for sparklyr to read data from Amazon Redshift into Spark DataFrames. It uses the Spark package spark-redshift to load redshift data into Spark DataFrames.

## Installation
sparkredshift requires the sparklyr package to run

### Install sparklyr
I recommend the latest stable version of sparklyr available on CRAN
```{r eval = FALSE}
install.packages("sparklyr")
```

### Install sparkredshift
Install the development version of sparkredshift from this Github repo using devtools
```{r eval = FALSE}
library(devtools)
devtools::install_github("emaasit/sparkredshift")
```

## Connecting to Spark

If Spark is not already installed, use the following sparklyr command to install your preferred version of Spark:
```{r eval = FALSE}
library(sparklyr)
spark_install(version = "2.0.0")
```

The call to `library(sparkredshift)` will make the sparkredshift functions available on the R search path and will also ensure that the dependencies required by the package are included when we connect to Spark.
```{r eval = FALSE}
library(sparkredshift) 
```

We can create a Spark connection as follows:
```{r eval = FALSE}
sc <- spark_connect(master = "local")
```

## Reading redshift files

sparkredshift provides the function `spark_read_redshift` to read redshift data files into Spark DataFrames. It uses a Spark package called spark-redshift. Here's an example.

```{r eval = FALSE}
mtcars_file <- system.file("extdata", "mtcars.redshift", package = "sparkredshift")

mtcars_df <- spark_read_redshift(sc, path = mtcars_file, table = "redshift_table")
mtcars_df
```

The resulting pointer to a Spark table can be further used in dplyr statements.
```{r eval = FALSE}
library(dplyr)
mtcars_df %>% group_by(cyl) %>%
  summarise(count = n(), avg.mpg = mean(mpg), avg.displacment = mean(disp), avg.horsepower = mean(hp))
```

## Logs & Disconnect

Look at the Spark log from R:
```{r eval = FALSE}
spark_log(sc, n = 100)
```

Now we disconnect from Spark:
```{r eval = FALSE}
spark_disconnect(sc)
```

## Acknowledgements
Thanks to RStudio for the sparklyr package that provides functionality to create Extensions.
